---
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# Wordmap: Semi-supervised Multinomial Document Classifier

**wordmap** is a semi-supervised algorithm for multinomial document classification originally created for [newsmap](https://github.com/koheiw/newsmap). **wordmap** is separated from **newsmap** to expand the score of its application beyond geographical classification of news. 

The algorithm is also useful in extracting features associated with document meta-data (industry group, patent class etc.) from vary larger corpora. The list of features could be used to create a lexicon to perform dictionary analysis.

## How to install

**wordmap** is available on CRAN since the v0.8.0 You can install the package using the R command.

```{r, eval=FALSE}
install.packages("wordmap")
```

If you want to the latest version, please install by running this command in R. You need to have **devtools** installed beforehand.

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("koheiw/wordmap")
```

## Example

In this example, we identify topics of sentences from using a seed topic dictionary adopted from [Watanabe & Zhou (2020)](https://journals.sagepub.com/doi/full/10.1177/0894439320907027).
`data_corpus_ungd2017` contains transcripts of speeches delivered at the United Nations General Assembly in 2017.

```{r}
require(quanteda)
require(wordmap)

dict <- data_dictionary_topic
print(dict)

corp <- data_corpus_ungd2017 %>% 
    corpus_reshape()

toks <- tokens(corp, remove_url = TRUE, remove_numbers = TRUE) %>% 
    tokens_remove(stopwords("en"), min_nchar = 2, padding = TRUE) #%>% 
    #tokens_remove("^[A-Z]", valuetype = "regex", case_insensitive = FALSE, padding = TRUE)
    
dfmt_feat <- dfm(toks, remove_padding = TRUE) %>% 
    dfm_trim(min_termfreq = 5)
dfmt_label <- tokens_lookup(toks, dict) %>% 
    dfm()

map <- textmodel_wordmap(dfmt_feat, dfmt_label)
coef(map)
```

### Predict topics of sentences 

```{r}
dat <- data.frame(text = corp, topic = predict(map))
```

```{r echo=FALSE}
knitr::kable(head(dat, 10))
```

### Create a topic dictionary

Create a **quanteda** dictionary object from the extracted features. The dictionary could be use to perform analysis of other corpora.

```{r}
as.dictionary(map, n = 100)
```
