---
output: github_document
---

```{r, echo=FALSE, message=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "##",
  fig.path = "man/images/"
)
```

# Wordmap: Semi-supervised Multinomial Document Classifier

**wordmap** is a naive Bayesian model for multinomial document classification originally created for [Newsmap](https://github.com/koheiw/newsmap). **wordmap** is separated from **newsmap** to expand the score of its application beyond geographical classification of news.

The semi-supervised classifier has been used to for various purposes such as classificaiton of [speeches in terms of topics](https://journals.sagepub.com/doi/full/10.1177/0894439320907027). The simplicity of naive Bayesian algorithm makes it useful for extracting features from vary larger corpora to create dictionaries The detail of the algorithm is explained in [Watanabe (2018)](https://www.tandfonline.com/eprint/dDeyUTBrhxBSSkHPn5uB/full). 

## How to install

**wordmap** is available on CRAN since the v1.0. You can install the package using the R command.

```{r, eval=FALSE}
install.packages("wordmap")
```

If you want to the latest version, please install by running this command in R. You need to have **devtools** installed beforehand.

```{r, eval=FALSE}
install.packages("devtools")
devtools::install_github("koheiw/wordmap")
```

## Example

`data_corpus_ungd2017` contains transcripts of speeches delivered at the United Nations General Assembly in 2017. The dictionary is adopted from [Watanabe & Zhou (2020)](https://journals.sagepub.com/doi/full/10.1177/0894439320907027).

```{r}
require(quanteda)
require(wordmap)

dict <- dictionary(file = "dict/dictionary.yml")
print(dict)

corp <- data_corpus_ungd2017 %>% 
    corpus_reshape()

toks <- tokens(corp, remove_url = TRUE, remove_numbers = TRUE) %>% 
    tokens_remove(stopwords("en"), min_nchar = 2, padding = TRUE)
    
dfmt_feat <- dfm(toks, remove_padding = TRUE)
dfmt_label <- tokens_lookup(toks, dict) %>% 
    dfm()

map <- textmodel_wordmap(dfmt_feat, dfmt_label)
coef(map)
```

### Predict topics of sentences 

```{r}
dat <- data.frame(text = corp, topic = predict(map))
```

```{r echo=FALSE}
knitr::kable(head(dat, 10))
```
### Create a topic dictionary

Create a **quanteda** dictionary object from the extracted features. The dictionary could be use to perform analysis of other corpora.

```{r}
as.dictionary(map, n = 100)
```
